#testing number of challenge wins as a factor in chance of winning

```{r}
# number of challenge wins per castaway
challenge_stats <- challenge_results |> 
  group_by(castaway_id) |> 
  summarise(
    won = sum(result == "Won"),
    total_challenges = n(),
    percentage_won = (won/total_challenges)
  )
glimpse(challenge_stats)
```

```{r}
# who won the most challenges
challenge_stats |>
  filter(percentage_won > .8)
```
#most challenge wins is Ozzy
#perfect challenge winns is Lilliana Gomez season 14  - her tribe chose to give up immunity and she was voted off

```{r}
summary(challenge_stats$percentage_won)
```

```{r}
# percentage of challenges won histogram
ggplot(data = challenge_stats, aes(x = percentage_won)) + geom_histogram()
```

```{r}
# number of challenge wins versus number of challenges competed in (per castaway)
ggplot(data = challenge_stats, aes(x = total_challenges, y = won)) + geom_point() + geom_smooth(method=lm, se=FALSE) + annotate("text",x=10, y=50, label = (paste0("slope==", coef(lm(challenge_stats$won~challenge_stats$total_challenges))[2])), parse=TRUE)
```

#non winners
```{r}
winner_list <- df %>%
  select(winner_id)

glimpse(winner_list)
```

```{r}
not_winners_challenge_stats <- challenge_stats %>%
  filter(!castaway_id %in% c(winner_list$winner_id))
glimpse(not_winners_challenge_stats)
```

```{r}
# percentage of challenges won histogram (non winners)
ggplot(data = not_winners_challenge_stats, aes(x = percentage_won)) + geom_histogram()
```

```{r}
# number of challenge wins versus number of challenges competed in (per non winning castaway)
ggplot(data = not_winners_challenge_stats, aes(x = total_challenges, y = won)) + geom_point() + geom_smooth(method=lm, se=FALSE) + annotate("text",x=10, y=50, label = (paste0("slope==", coef(lm(not_winners_challenge_stats$won~not_winners_challenge_stats$total_challenges))[2])), parse=TRUE)
```

```{r}
df <- season_summary %>% 
     left_join(challenge_results, by = c("winner_id" = "castaway_id"))
```

#df table has episode summaries for season winners

```{r}
# number of challenge wins per winning castaway
winners_challenge_stats <- df |> 
  group_by(version_season.x) |> 
  summarise(
    won = sum(result == "Won"),
    total_challenges = n(),
    percentage_won = (won/total_challenges)
  )
glimpse(winners_challenge_stats)
```

```{r}
view(df)
```

```{r}
# who won the most challenges
winners_challenge_stats |>
  filter(won > 30)
```

```{r}
# number of challenge wins versus number of challenges competed in (per castaway)
ggplot(data = winners_challenge_stats, aes(x = total_challenges, y = won)) + geom_point() + geom_smooth(method=lm, se=FALSE) + annotate("text",x=20, y=50, label = (paste0("slope==", coef(lm(winners_challenge_stats$won~winners_challenge_stats$total_challenges))[2])), parse=TRUE)
```

```{r}
# percentage of challenges won for winners histogram
ggplot(data = winners_challenge_stats, aes(x = percentage_won)) + geom_histogram()
```

```{r}
summary(challenge_stats$percentage_won)
```
#Robert "Bob" Crowley season 17 had highest percentage - 63.64%
#Natalie white season 19 had lowest percentage - 13.04%

Ho: mean challenge wins for winners (pw) is the same as overall mean challenge wins (pt)

```{r}
pw = mean(winners_challenge_stats$percentage_won, trim = 0, na.rm = TRUE)
nw = 60
```

```{r}
pt = mean(not_winners_challenge_stats$percentage_won, trim = 0, na.rm = TRUE)
nt = 899
```

```{r}
p_pool = (nw*pw + nt*pt)/(nw+nt)
```

```{r}
SE = sqrt(p_pool*(1 - p_pool)*((1/nw) + (1/nt)))
```

```{r}
z = ((pw-pt)-0)/SE
```

```{r}
p_value = 2*(1-pnorm(z,0,1))
```

#p_value = .997 so Ho is rejected
#therefore, number of challenge wins has an impact on your chances of winning

```{r}
SE_CI = sqrt(((pw*(1-pw))/nw) + ((pt*(1-pt))/nt))
```

```{r}
z_star = qnorm(.95 + (.05/2), 0, 1)
```

```{r}
ME = z_star*SE_CI
```

```{r}
CI_lower = pw-pt - ME
```

```{r}
CI_upper = pw-pt + ME
```
